---
title: "MCG assessment of Kamvar et al 2017"
author: "Zhian N. Kamvar"
date: "`r Sys.Date()`"
output: github_document
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(width = 90)
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = TRUE)
```

Introduction
=============

This document will test the hypothesis that mycelial compatibility groups will
deliniate sexually recombining populations of *Sclerotinia sclerotiorum*. In
this document, we are using data from @kamvar2017data, which consists of 366
isolates of *S. sclerotiorum* sampled over 11 states in the United States of
America, as well as Australia, France, and Mexico.

If this hypothesis is true, we expect to find no signatures of linkage within
the data before or after clone correction. We will be measuring clone-correction
via the standardized index of association, $\bar{r}_d$ as implemented in the
*poppr* package [@agapow2001indices; @kamvar2014poppr].

Packages and Data
-----------------

Here we are loading the data and packages necessary for the analyses. 

```{r, message = FALSE, warning = FALSE}
library("poppr")
library("tidyverse")
library("ggridges")
library("ape")
library("cowplot")
library("gridGraphics")
```

Now that the packages are loaded, we can load the data:

```{r}
data_cols <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)
dat <- readr::read_csv(here::here("data/kamvar2017population.csv"), col_types = data_cols)
dat
```

Since these are the data for the 16 loci, we only want to keep the 11 that were
used for the study:

```{r}
replen <- c(
"5-2(F)" = 2,
"5-3(F)" = 4,
"6-2(F)" = 5.99999,
"7-2(F)" = 2,
"8-3(H)" = 2,
"9-2(F)" = 2,
"12-2(H)" = 2,
"17-3(H)" = 3,
"20-3(F)" = 2,
"36-4(F)" = 4,
"50-4(F)" = 4,
"55-4(F)" = 4,
"92-4(F)" = 2,
"106-4(H)" = 4,
"110-4(H)" = 3.99999,
"114-4(H)" = 4
)
loci_to_keep <- c("5-2(F)", "6-2(F)", "7-2(F)", "8-3(H)", "9-2(F)", "12-2(H)", 
"17-3(H)", "20-3(F)", "55-4(F)", "110-4(H)", "114-4(H)")
```

Now we can use these to subset our data:

```{r}
dat11 <- dat %>% 
  select(loci_to_keep) %>%
  df2genind(strata = select(dat, Region, Source, Host, MCG, Year), 
            ind.names = dat$Isolate,
            ploidy = 1) %>%
  as.genclone()
stopifnot(nLoc(dat11) == 11L)
stopifnot(nmll(dat11) == 165L)
other(dat11)$REPLEN <- replen
other(dat11)$meta <- dat %>% select(Severity, Isolate)
setPop(dat11) <- ~Region
dat11
```

Index of Association
====================

By MCG
--------

When we assess this by MCG, we need to first ensure that we are not drastically
reducing our sample size because there is evidence that small sample sizes
reduces the power of the index of association and can make clonal populations
appear to be sexual.

```{r by-mcg, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```

In terms of our hypothesis, that was underwhelming... What happens if we clone
correct our data? We'll use the scheme in [@kamvar2017data], adding MCG as the
highest level:

```{r by-mcg-cc, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  clonecorrect(~MCG/Region/Source/Host/Year, keep = 1) %>%
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```

Okay, maybe that heirarchy is a bit... detailed. What happens if we go the
opposite way? What if we simply clone-corrected just on MCG?

```{r by-mcg-cc-bomb, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  clonecorrect(~MCG) %>% 
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```


Okay. So far, we have no evidence for this hypothesis. But one of the issues
that we saw in Kamvar et al. 2017 was that these data reflected a clonal
population structure. One thing that I'm curious about is the results that were
obtained by @prugnolle2010apparent showing that individuals sampled from 
differentiated populations will have a lower index of association. I can test
this by simulating data.


Data Simulations
----------------

I've written a simulator in an R package called "kop" and am loading it here:

```{r load-pg}
library("doParallel")
library("kop")
```

First step is to create some populations. Because I want to get a representative
from each population, I'm going to create 20 populations. These populations are
initially simulated from a multinomial distribution, but this often results in
extremely long branches for a tree:

```{r example_sim}
kop::pop_generator(mate_gen = 0, mu = 0.5) %>% 
  aboot(sample = 1, tree = "nj", dist = "dist", quiet = TRUE) %>%
  invisible()
```


To avoid this, I'm parameterizing the simulations thusly:

| Parameter | Value |
| --------- | ----- |
| Census Size | 1000 |
| Sample Size | 100 |
| Generations of random mating | 400 |
| Generations of clonal reproduction (after random mating) | 100 |
| Mutations/Generation (over all samples/loci) | 0.5 |

The random mating serves to shorten those long terminal branches. This is
important for ensuring that the populations we DO simulate are sufficiently 
different from each other.

```{r create-population, cache = TRUE}
cl <- makeCluster(4)
registerDoParallel(cl, cores = 4)
set.seed(2017-11-21)
test <- foreach(seq_len(20), .combine = c, .packages = c("kop", "poppr", "dplyr", "purrr", "tibble")) %dopar% 
  pop_generator(n = 1000, mate_gen = 400, clone_gen = 100, mu = 0.5, verbose = FALSE)
stopCluster(cl)
test <- test %>%
  repool() %>%
  as.genclone()
strata(test) <- data.frame(pop = pop(test))
```

```{r poptree, cache = TRUE}
test
nAll(test)
plot(ape::nj(diss.dist(test, percent = TRUE)), lab4ut = "axial", type = "unrooted", tip.col = adegenet::funky(nPop(test))[pop(test)])
```


We can see from this that the clonal reproduction reduced the number of unique
individuals quite a bit. If we test the index of association for these
populations, we can see that they are indeed clonal:

```{r ia-sims, cache = TRUE, dependson = "create-population"}
poppr(test, total = FALSE, sample = 999) 
poppr(test, clonecorrect = TRUE, total = FALSE, strata = ~pop, sample = 999)
```

We can see how they all are related (or not so) to each other

```{r ia-aboot, cache = TRUE, dependson = "create-population"}
aboot(test, ~pop, sample = 1000, dist = "nei.dist", tree = "nj")
```

Now that we've set up the popualtions, we can randomly sample two individuals
from each and pool them together.

```{r resample_popualtions, cache = TRUE, dependson = "create-population"}
# Sample one individual per population
sample_one <- quote(flatten_dbl(map(popNames(test), ~{ sample(which(pop(test) == .), 1) })))
subsamples <- replicate(100, test[eval(sample_one), ])
```

```{r calculate_ia, cache = TRUE, dependson = "resample_populations"}
cl <- makeCluster(4)
registerDoParallel(cl, cores = 4)
set.seed(2017-11-21)
res <- foreach(i = seq(subsamples), .combine = c, .packages = c("poppr")) %dopar% 
  list(ia(subsamples[[i]], sample = 999, valuereturn = TRUE, plot = FALSE, quiet = TRUE))
stopCluster(cl)

# reshaping everything into a data frame
resdf <- map(res, 1) %>% 
  map(as.list) %>% 
  bind_rows()
(resdf <- bind_cols(resdf, data_frame(sims = map(res, 2))))
```


> This simulation take a long time to run. When you come back to it, use the 
> function `lazierLoad("cache")` to reload all of the saved results:
> `source("https://gist.githubusercontent.com/zkamvar/655be26d1d5bec1ac948/raw/97db57030d016a0e7a8156aa84ad02a7c8bc644c/lazierLoad.R")`

Now we can see what fraction of the simulations resulted in a significant value
of $\bar{r}_d$

```{r, dependson = "resample_populations"}
sum(resdf$p.rD <= 0.05)/nrow(resdf)
```

That's not very many.

What do the data look like:

```{r fig.width = 10, fig.height = 5, dependson = "resample_populations"}
ccia <- poppr(test, quiet = TRUE, total = FALSE)
the_plot <- resdf %>% 
  ggplot(aes(x = rbarD, fill = p.rD >= 0.05)) + 
  geom_histogram(binwidth = 0.01, position = "stack", color = "black") +
  geom_rug(aes(color = p.rD)) +
  viridis::scale_color_viridis() +
  scale_fill_manual(values = c("grey30", "grey80")) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  labs(list(
    fill = expression(paste("p >= 0.05")),
    color = "p-value",
    x = expression(paste(bar(r)[d])),
    title = "The index of association of mixed population samples",
    subtitle = "100 replicates; 20 populations; 1 individual from each population",
    caption = expression(paste("(dashed lines: observed ", bar(r)[d], " values)"))
  ))
the_plot + geom_vline(xintercept = ccia$rbarD, lty = 3)
```


What happens when we randomly sample 20 individuals from each population?

```{r randsamp, fig.width = 10, fig.height = 5, cache = TRUE, dependson = "resample_populations"}
set.seed(2017-12-04)
resampled_rbarD <- seppop(test) %>%
  map_df(resample.ia, n = 20, .id = "Population") %>%
  as_tibble()
resampled_rbarD_res <- resampled_rbarD %>% 
  group_by(Population) %>% 
  summarize(rbarD = mean(rbarD)) %>% 
  pull(rbarD)
the_plot + 
  geom_vline(xintercept = resampled_rbarD_res, lty = 3) +
  labs(caption = expression(paste("(dashed lines: resampled ", bar(r)[d], " values)")))
```


# Attempting to make pretty plots


Because the ulitmate goal here is to make graphics that may be understandable,
I'm goint to attempt to create a ridgeline density plot of $\bar{r}_d$ values
and combine that with a tree of the 20 random samples overlayed on random
samples from all populations.

```{r fig.width = 3.5, fig.height = 5}
ridgelines <- resdf %>% 
  select(Ia, rbarD) %>% 
  add_column(Population = "pooled") %>% 
  bind_rows(resampled_rbarD, .id = "Data") %>% 
  mutate(Data = case_when(Population == "pooled" ~ "pooled", TRUE ~ "single")) %>% 
  mutate(Population = case_when(
           grepl("unknown", Population) ~ sprintf("pop %2d", as.integer(gsub("unknown_", "", Population))),
           TRUE ~ Population
           )) %>% 
  group_by(Population) %>% 
  mutate(m = mean(rbarD)) %>% 
  arrange(m) %>% 
  select(-m) %>% 
  ungroup() %>% 
  mutate(Population = fct_inorder(Population))

p_ridge <- ggplot(ridgelines, aes(x = rbarD, y = Population, fill = Data, height = ..density..)) + 
  geom_density_ridges(scale = 5) +
  theme_ridges(font_size = 16, font_family = "Helvetica", grid = TRUE, center_axis_labels = TRUE) +
  scale_x_continuous(limits = c(NA, 0.4), breaks = c(0, 0.2, 0.4)) +
  scale_y_discrete(expand = c(0.01, 0)) +
  theme(aspect.ratio = 1.25) +
  theme(legend.position = "top") +
  theme(legend.justification = "center") +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks.y = element_blank()) +
  theme(axis.ticks.x = element_blank()) +
  theme(axis.title.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.major.x = element_line(linetype = 3, color = "grey50")) +
  scale_fill_manual(values = c("grey20", "grey80")) +
  labs(list(
    x = expression(paste(italic(bar(r)[d])))
  ))
p_ridge
ggsave(p_ridge, filename = here::here("results/figures/p-ridge.pdf"))
```


Here we need to create a tree that is digestable, which means creating one that
we can easily label. I am first taking one of the data sets that had random
subsamples and am resampling 19 individuals from each of the 20 populations and
creating a tree from the resulting 400 individuals. From this tree, I will
highlight the edges that are found in the subsample and compare those to the
trees created from within-population subsample.

```{r treecomparison, fig.width = 6, fig.height = 3.5}
s1 <- subsamples[[1]]
set.seed(2017-12-04)
samps <- data_frame(pop = pop(test), ind = indNames(test)) %>% 
  filter(!ind %in% indNames(s1)) %>%
  group_by(pop) %>%
  sample_n(19) %>%
  bind_rows(unsampled = ., sampled = data_frame(pop = pop(s1), ind = indNames(s1)), .id = "tree")

ftree  <- diss.dist(test[samps$ind], percent = TRUE) %>% nj()
cols    <- setNames(adegenet::funky(nPop(test)), popNames(test))
fullcol  <- samps %>% mutate(cols = case_when(tree == "sampled" ~ cols[pop], TRUE ~ transp(cols[pop], 0.5))) %>% pull(cols)
fullsize <- samps %>% mutate(cols = case_when(tree == "sampled" ~ 2, TRUE ~ 0.5)) %>% pull(cols)
newedge <- seq(ftree$edge) %in% which.edge(ftree, tail(samps$ind, 20))
ew      <- ifelse(newedge, 2, 1)
ec      <- ifelse(newedge, "black", transp("grey50", 0.5))
maintree <- function(){
  plot.phylo(ftree, 
             type = "unrooted", 
             show.tip.label = FALSE, 
             no.margin = TRUE, 
             edge.width = ew, 
             edge.color = ec)
  tiplabels(pch = 21, bg = fullcol, col = NA, cex = fullsize)
  add.scale.bar(length = 0.1, lwd = 2)
}
subtrees <- function(){
  for (i in popNames(test)){
    inds <- samps$ind[samps$pop == i]
    test[inds] %>% 
      diss.dist(percent = TRUE) %>%
      nj() %>%
      plot.phylo(type = "unrooted", 
                 show.tip.label = FALSE, 
                 no.margin = TRUE, 
                 edge.width = 2,
                 edge.color = cols[i])
    add.scale.bar(length = 0.1, lwd = 2)
  }
}
treeplot <- function(){
  m <- matrix(c(rep(1, 20), 2:21), nrow = 4, ncol = 10)
  l <- layout(m)
  maintree()
  subtrees()
  layout(matrix(1, 1, 1))
}
treeplot()
pdf(here::here("results/figures/treeplot.pdf"), width = 6, height = 3.5)
treeplot()
dev.off()
```

I can use plot_grid from cowplot to combine the main tree and the ridgeline density plot.

```{r fig.width = 6, fig.height = 3.5}
p <- plot_grid(maintree, p_ridge + theme(legend.position = "none"), scale = c(0.8, 1), labels = "AUTO")
ggsave(filename = here::here("results/figures/iatree.pdf"), plot = p, width = 6, height = 3.5)
```



<details>
<summary>Session Information</summary>

```{r}
devtools::session_info()
```

</details>

References
==========