---
title: "MCG assessment of Kamvar et al 2017"
author: "Zhian N. Kamvar"
date: "`r Sys.Date()`"
output: github_document
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(width = 90)
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = TRUE)
```

Introduction
=============

This document will test the hypothesis that mycelial compatibility groups will
deliniate sexually recombining populations of *Sclerotinia sclerotiorum*. In
this document, we are using data from @kamvar2017data, which consists of 366
isolates of *S. sclerotiorum* sampled over 11 states in the United States of
America, as well as Australia, France, and Mexico.

If this hypothesis is true, we expect to find no signatures of linkage within
the data before or after clone correction. We will be measuring clone-correction
via the standardized index of association, $\bar{r}_d$ as implemented in the
*poppr* package [@agapow2001indices; @kamvar2014poppr].

Packages and Data
-----------------

Here we are loading the data and packages necessary for the analyses. 

```{r, message = FALSE, warning = FALSE}
library("poppr")
library("tidyverse")
```

Now that the packages are loaded, we can load the data:

```{r}
data_cols <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)
dat <- readr::read_csv(here::here("data/kamvar2017population.csv"), col_types = data_cols)
dat
```

Since these are the data for the 16 loci, we only want to keep the 11 that were
used for the study:

```{r}
replen <- c(
"5-2(F)" = 2,
"5-3(F)" = 4,
"6-2(F)" = 5.99999,
"7-2(F)" = 2,
"8-3(H)" = 2,
"9-2(F)" = 2,
"12-2(H)" = 2,
"17-3(H)" = 3,
"20-3(F)" = 2,
"36-4(F)" = 4,
"50-4(F)" = 4,
"55-4(F)" = 4,
"92-4(F)" = 2,
"106-4(H)" = 4,
"110-4(H)" = 3.99999,
"114-4(H)" = 4
)
loci_to_keep <- c("5-2(F)", "6-2(F)", "7-2(F)", "8-3(H)", "9-2(F)", "12-2(H)", 
"17-3(H)", "20-3(F)", "55-4(F)", "110-4(H)", "114-4(H)")
```

Now we can use these to subset our data:

```{r}
dat11 <- dat %>% 
  select(loci_to_keep) %>%
  df2genind(strata = select(dat, Region, Source, Host, MCG, Year), 
            ind.names = dat$Isolate,
            ploidy = 1) %>%
  as.genclone()
stopifnot(nLoc(dat11) == 11L)
stopifnot(nmll(dat11) == 165L)
other(dat11)$REPLEN <- replen
other(dat11)$meta <- dat %>% select(Severity, Isolate)
setPop(dat11) <- ~Region
dat11
```

Index of Association
====================

By MCG
--------

When we assess this by MCG, we need to first ensure that we are not drastically
reducing our sample size because there is evidence that small sample sizes
reduces the power of the index of association and can make clonal populations
appear to be sexual.

```{r by-mcg, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```

In terms of our hypothesis, that was underwhelming... What happens if we clone
correct our data? We'll use the scheme in [@kamvar2017data], adding MCG as the
highest level:

```{r by-mcg-cc, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  clonecorrect(~MCG/Region/Source/Host/Year, keep = 1) %>%
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```

Okay, maybe that heirarchy is a bit... detailed. What happens if we go the
opposite way? What if we simply clone-corrected just on MCG?

```{r by-mcg-cc-bomb, cache = TRUE}
dat11 %>% 
  setPop(~MCG) %>%                   # set population to MCGs
  selPopSize(n = 10) %>%             # constrain to 10 samples per population
  clonecorrect(~MCG) %>% 
  poppr(sample = 999, total = FALSE) # test index of association for each pop
```


Okay. So far, we have no evidence for this hypothesis. But one of the issues
that we saw in Kamvar et al. 2017 was that these data reflected a clonal
population structure.  


<details>
<summary>Session Information</summary>

```{r}
devtools::session_info()
```

</details>

References
==========